### 2016-03-09 paper/stereo.tex
yasu

\section{Implementation details}
\subsection{Stereoo}

>>>>

\section{Swarm Fusion implementations}
We now explain detailed implementation of the Swarm Fusion method for
three problems in Computer Vision.

\subsection{Swarm Fusion stereo}
We start with a simple Swarm Fusion implementation for a standard stereo
problem with unary and pairwise (submodular) terms.
